\documentclass[]{tufte-handout}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{bibentry}

\title{COMP 343: Reading Assignments}
\author{  }
\date{Fall 2016}

\begin{document}
\nobibliography{comp343.bib}
\maketitle

\begin{abstract}
  One goal of this course is to develop your ability navigate the primary sources of computing: journal and conference papers. Towards this end you'll be reading and reporting on at least a paper per chapter covered. This document describes what you need to submit for every paper in order to get credit for the reading as well as how reading assignments will be graded.
\end{abstract}

\section{How to Read}

We'll be using Keshav's three-pass approach in this class\cite{Keshav}. We'll discuss this approach on day one. For the most part, you'll only be doing two-pass readings. A full third-pass will on be necessary for one or two papers relative to your literature review.

\section{What to Turn In}

For each reading assignment you will turn in a one two two page report containing:
\begin{itemize}
  \item \textit{The five Cs}: \newline After the first pass reading you should be able to produce the five Cs. Your focus should first and foremost be on Context and Contributions. Once you understand what's being said in the paper and the context from which it arose, then comment on clarity and correctness. Finally, categorize the paper as best as possible.
  \item \textit{A Summary}: \newline After the second pass you should be able to provide a brief, one to two paragraph summary of the paper's content \textit{in your own words}.
\end{itemize}

\section{Papers}

You'll be reading the following papers in the following order. For due dates see the syllabus.

\begin{enumerate}
  \item \bibentry{Turing}
  \item \bibentry{Horvitz}
  \item \bibentry{KorfSchultze}
  \item \bibentry{MintonEtAl}
  \item \bibentry{FrankEtAl}
  \item \bibentry{Pearl}
  \item \bibentry{SilverEtAl}
\end{enumerate}

\newpage

\section{Grading}

Reading reports are graded on a three point scale. To earn a three you must clearly identify and report on the paper's contributions and context.  Additionally, the summary must hit upon the main points and evidence provided in the paper using your own words.  A score of two means critical parts of the paper weren't addressed or the overall report seems to restate elements of the paper rather than provide an external summary.  A score of one typically means the report either missed the point of the paper or  seems to just be a rehash of the paper, borrowing too heavily from the authors' words and not written in your own voice. Scores will be averaged together and the final reading assignment grade is determined based on the scale given in table~\ref{scores}.

\begin{table}[!htbp]
\begin{center}
\begin{small}
\begin{tabular}{ll}
Assignment Avg. (Min) & Letter Grade \\ \toprule
2.7   & A  \\
2.5    & A- \\
2.4 & B+ \\
2.1    & B  \\
2   & B- \\
1.7    & C+ \\
1.5 & C  \\
1   & C- \\
0.7    & D  \\
< 0.7  & F
\end{tabular}
\end{small}
\end{center}
\caption{Grading Scale for Reading Reports}
\label{scores}
\end{table}

\bibliographystyle{acm}
\end{document}
